Active Learning for Level Set Estimation

### 2013-05-01 ijcai13pres.tex
Minor fix
Most of the changes discussed with Andreas

@@

\date[IJCAI 2013]{
IJCAI 2013
}

@@

\begin{frame}{Outline}
  \tableofcontents
  % You might wish to add the option [pausesections]
\end{frame}

@@

\begin{frame}
\begin{itemize}
\item<1-> Pose as a sequential decision making problem (\emph{pool-based active learning}):
\begin{itemize}
\item<2-> No measurements available in advance, just a set (pool) of possible sampling locations ($D$)
\vspace{0.5em}
\item<3->[]\hspace{-1.5em} At each iteration $t \geq 1$:
\item<3-> Decide where to measure next ($x_t$)
\item<4-> Obtain noisy observation ($y_t = f(x_t) + n_t$)
\item<5-> Update our estimate of the underlying function
\end{itemize}
\end{itemize}
\begin{center}
\color{white}
\includegraphics<1>[draft,width=4.45in]{figures/oned_0}
\color{black}
\includegraphics<2>[width=4.45in]{figures/oned_0}
\includegraphics<3>[width=4.45in]{figures/oned_1_0}
\includegraphics<4>[width=4.45in]{figures/oned_1_1}
\includegraphics<5>[width=4.45in]{figures/oned_1_2}
\includegraphics<6>[width=4.45in]{figures/oned_2_0}
\includegraphics<7>[width=4.45in]{figures/oned_2_1}
\includegraphics<8>[width=4.45in]{figures/oned_2_2}
\end{center}
\end{frame}

@@

\begin{frame}
\begin{center}
\uncover<1->{\large Why GPs are nice}
\end{center}
\begin{itemize}
\item<2-> \textbf{Nonparametric}:\\
      Impose ``smoothness'' assumptions via kernel $k(x, x')$.
\vspace{1em}
\item<3-> \textbf{Bayesian}, yet \textbf{efficient}:
      \begin{align*}
        \mu_t(\*x) &= \*k_t(\*x)^T\left(\*K_t + \sigma^2 \*I\right)^{-1}\*y_t\\
        k_t(\*x, \*x') &= k(\*x, \*x') - \*k_t(\*x)^T\left(\*K_t + \sigma^2 \*I\right)^{-1}\*k_t(\*x)\notag\\
        \sigma_t^2(\*x) &= k_t(\*x, \*x)
      \end{align*}
      Suitable for step-by-step updates.
\vspace{1em}
\item<4-> They provide \textbf{variance estimates}!\\
          Construct confidence intervals: $Q_t(\*x) = \left[\mu_{t-1}(\*x) \pm \beta_t^{1/2} \sigma_{t-1}(\*x)\right]$
\end{itemize}
\end{frame}

\begin{frame}
\begin{center}
\includegraphics<1>[width=4.45in]{figures/voned_0}
\includegraphics<2>[width=4.45in]{figures/voned_1_0}
\includegraphics<3>[width=4.45in]{figures/voned_1_1}
\includegraphics<4>[width=4.45in]{figures/voned_1_2}
\includegraphics<5>[width=4.45in]{figures/voned_2_0}
\includegraphics<6>[width=4.45in]{figures/voned_2_1}
\includegraphics<7>[width=4.45in]{figures/voned_2_2}
\includegraphics<8>[width=4.45in]{figures/voned_3_0}
\includegraphics<9>[width=4.45in]{figures/voned_3_1}
\includegraphics<10>[width=4.45in]{figures/voned_3_2}
\end{center}
\end{frame}

\begin{frame}
\begin{enumerate}
\item<1-> How do we \textbf{estimate} the function? \uncover<3->{\Large\color{green!70!black}\checkmark}
\vspace{0em}
\item<4-> How do we \textbf{classify}? \uncover<14->{\Large\color{green!70!black}\checkmark}
\vspace{0.3em}
\item<15-> How do we \textbf{select} ``informative'' measurements? \uncover<24->{\Large\color{green!70!black}\checkmark}
\uncover<16->{
\begin{itemize}
\item<16-> Pick among the yet unclassified.
\item<17-> Doesn't really matter which!\\
           \uncover<18->{(e.g. max. variance, }\uncover<19->{max. ambiguity}\uncover<23->{, or even random)}
\end{itemize}}
\end{enumerate}

\begin{center}
\color{white}
\includegraphics<1>[draft,width=3.5in]{figures/voned_cl_00}
\color{black}
\includegraphics<2-4>[width=3.5in]{figures/voned_cl_00}
\includegraphics<5>[width=3.5in]{figures/voned_cl_01}
\includegraphics<6>[width=3.5in]{figures/voned_cl_10}
\includegraphics<7>[width=3.5in]{figures/voned_cl_11}
\includegraphics<8>[width=3.5in]{figures/voned_cl_20}
\includegraphics<9>[width=3.5in]{figures/voned_cl_21}
\includegraphics<10>[width=3.5in]{figures/voned_cl_30}
\includegraphics<11>[width=3.5in]{figures/voned_cl_31}
\includegraphics<12>[width=3.5in]{figures/voned_cl_40}
\includegraphics<13-19>[width=3.5in]{figures/voned_cl_41}
\includegraphics<20>[width=3.5in]{figures/voned_cl_41_amb_0}
\includegraphics<21>[width=3.5in]{figures/voned_cl_41_amb_1}
\includegraphics<22->[width=3.5in]{figures/voned_cl_41_amb_2}
\end{center}
\end{frame}

@@

\begin{frame}
\begin{columns}[t]
\column{0.45\textwidth}
{\footnotesize
\begin{algorithmic}
  \REQUIRE sample set $D$, GP prior ($\mu_0$, $k$, $\sigma_0$),\\
           \hspace{2.2em}thr. value $h$, accuracy parameter $\epsilon$
  \ENSURE predicted sets $\hat{H}$, $\hat{L}$
  \uncover<2->{
  \CSTATE{c1}$H_0 \gets \varnothing$,\enskip $L_0 \gets \varnothing$,\enskip $U_0 \gets D$ \label{lin:init1}
  %\LET{$H_0$}{$\varnothing$} \label{lin:init1}
  %\LET{$L_0$}{$\varnothing$}
  %\LET{$U_0$}{$D$}
  \CLET{c1}{$C_0(\*x)$}{$\mathbb{R}$, for all $\*x \in D$} \label{lin:init2}
  \CLET{c1}{$t$}{1}
  }
  \uncover<3->{
  \CWHILE{c6}{$U_{t-1} \neq \varnothing$}
    \CSTATE{c6}$H_t \gets H_{t-1}$,\enskip $L_t \gets L_{t-1}$,\enskip $U_t \gets U_{t-1}$
    }
    %\LET{$H_t$}{$H_{t-1}$}
    %\LET{$L_t$}{$L_{t-1}$}
    %\LET{$U_t$}{$U_{t-1}$}
    \uncover<4->{
    \CFORALL{c2}{$\*x \in U_{t-1}$}
      \CLET{c2}{$C_{t}(\*x)$}{$C_{t-1}(\*x) \cap Q_t(\*x)$} \label{lin:upd}
      \CIF{c2}{$\min(C_t(\*x)) + \epsilon > h$} \label{lin:class1}
        \CLET{c2}{$U_t$}{$U_t \setminus \{\*x\}$}
        \CLET{c2}{$H_t$}{$H_t \cup \{\*x\}$} 
      \CELSIF{c2}{$\max(C_t(\*x)) - \epsilon \leq h$} \label{lin:classr2}
        \CLET{c2}{$U_t$}{$U_t \setminus \{\*x\}$}
        \CLET{c2}{$L_t$}{$L_t \cup \{\*x\}$}
      \CENDIF{c2} \label{lin:class2}
    \CENDFOR{c2}
    }
    \uncover<5->{
    \CLET{c3}{$\*x_t$}{$\argmax \{a_t(\*x)\mid \*x \in U_t\}$} \label{lin:sel1}
    \CLET{c3}{$y_t$}{$f(\*x_t) + n_t$} \label{lin:sel2}
    }
    \uncover<6->{
    \CSTATE{c4}Compute $\mu_t(\*x)$ and $\sigma_t(\*x)$, $\forall\*x \in U_t$ \label{lin:inf}
    }
    \uncover<3->{
    \CLET{c6}{$t$}{$t + 1$}
  \CENDWHILE{c6}
  }
  \uncover<2->{
  \CLET{c5}{$\hat{H}$}{$H_{t-1}$} \label{lin:ret1}
  \CLET{c5}{$\hat{L}$}{$L_{t-1}$} \label{lin:ret2}
  }
\end{algorithmic}
}
\column{0.55\textwidth}
\begin{center}
The Level Set Estimation (\acl) algorithm
\end{center}
\only<3-6>{\vspace{34pt}$\leftarrow$ {\small loop until all points have been classified\\}\vspace{40pt}}
\only<4-6>{$\leftarrow$ {\small classify\\}\vspace{52pt}}
\only<5-6>{$\leftarrow$ {\small select max. ambiguity point\\}\vspace{3pt}}
\only<6>{$\leftarrow$ {\small update GP estimate}}
\only<7->{
\vspace{3pt}
\begin{itemize}
\only<7->{
\item Monotonicity of
\begin{enumerate}
\item confidence intervals
\item classification
\end{enumerate}
}
\vspace{0em}
\only<8->{
\item Relaxed classification rules by an accuracy parameter $\epsilon$\\
      (trades off sampling cost for accuracy)
}
\end{itemize}
}
\begin{center}
\includegraphics<8->[width=2in]{figures/voned_cl_41_eps}
\end{center}
\end{columns}
\end{frame}

@@

\subsection*{Results}
\begin{frame}
\begin{center}
{\large Experiments}
\end{center}
\begin{enumerate}
\item \acl
\item<2-> Maximum variance sampling:
\vspace{-0.5em}
\begin{align*}
\*x_t = \argmax_{\*x\in D} \sigma_{t-1}(\*x)
\end{align*}
\item<3-> ``Straddle'' heuristic (Bryan \emph{et al.}, 2005):
\vspace{-0.5em}
\begin{align*}
%\*x_t &= \argmax_{\*x\in D} 1.96\sigma_{t-1}(\*x)-|\mu_{t-1}(\*x) - h|\\
\*x_t \approx \argmax_{\*x\in D} a_{t-1}(\*x) \tag{for $\beta_t^{1/2} = 1.96$}
\end{align*}
\end{enumerate}
\end{frame}

\begin{frame}
\begin{center}
\hspace{4pt}\includegraphics<1->[width=4in]{figures/limno_chl_ls}\\[0.5em]
\uncover<2->{\includegraphics[width=2.3in]{figures/ev_chl_eps}}
\uncover<3->{\includegraphics[width=2.3in]{figures/ev_chl_seq}}
\end{center}
\end{frame}

\begin{frame}
\begin{center}
\includegraphics<1->[width=4in]{figures/limno_bgape_ls}\\[0.5em]
\color{white}
\only<1>{\includegraphics[draft,width=2.3in]{figures/ev_bgape_seq}}
\color{black}
\only<2-4>{\includegraphics[width=2.3in]{figures/ev_bgape_seq}}
\color{white}
\only<2>{\includegraphics[draft,width=2.3in]{figures/ev_bgape_eps}}
\color{black}
\only<3>{\includegraphics[width=2.3in]{figures/ev_bgape_eps}}
\only<4>{\includegraphics[width=2.3in]{figures/ev_bgape_seq_str_sc}}
\only<5>{\hspace{-16pt}\includegraphics[width=3.77in]{figures/limno_bgape_class_354}}
\only<6>{\hspace{-16pt}\includegraphics[width=3.77in]{figures/limno_bgape_str_class_400}}
\only<7>{\hspace{-16pt}\includegraphics[width=3.77in]{figures/limno_bgape_var_class_400}}
\end{center}
\end{frame}

@@

\begin{frame}
\begin{itemize}
\item<1-> What if we don't know $h$?
\vspace{1em}
\item<2-> Implicitly define the threshold level: $h = \omega \max_{\*x\in D} f(\*x),\ 0 < \omega < 1$
\vspace{1em}
\item<3-> \iacl:
\begin{itemize}
\item<4-> Need to also estimate the maximum
\item<5-> Slower classification due to uncertainty about $h$
\end{itemize}
\end{itemize}
\begin{center}
%\color{white}
%\only<1-2>{\includegraphics[draft,width=3.77in]{figures/voned_cl_41_imp_1}}
%\color{black}
%\only<3>{\includegraphics[width=3.77in]{figures/voned_cl_41_imp_1}}
%\only<4->{\includegraphics[width=3.77in]{figures/voned_cl_41_imp_2}}
\end{center}
\end{frame}

@@

\begin{frame}
\begin{itemize}
\item<1-> Up to this point we have assumed a fixed cost per sample
\item<2-> What about the traveling distance between measurements?
\item<3-> Plan ahead:
\begin{itemize}
\item Select a \emph{batch} of sampling locations (\bacl)
\item Connect them using a Euclidean TSP path
\item Traverse path and collect measurements
\end{itemize}
\end{itemize}

@@

\begin{frame}
\begin{center}
\large Geolocating internet latency
\end{center}
\begin{itemize}
\item<1-> Which world regions have low enough latency (e.g. < $150$ ms)
      for video chatting, online gaming, etc.?
\item<2-> Ideal setting for batch sampling $\rightarrow$ multiple pings in parallel
\end{itemize}
\begin{center}
\color{white}
\includegraphics<1-2>[draft,height=2.5in]{figures/map}
\color{black}
\includegraphics<3>[height=2.5in]{figures/map}
\includegraphics<4>[height=2.5in]{figures/map_ls_150}
\end{center}
\end{frame}

@@

\begin{frame}
\begin{center}
\large Questions?\\
\vspace{2em}
\sig{\includegraphics[width=3.5in]{figures/dilbert}}{www.dilbert.com}
\end{center}
\end{frame}

>>>>

\usepackage{grfext}\PrependGraphicsExtensions*{.png,.PNG}

%\usepackage{graphicx}
%\usepackage{epstopdf}
%\epstopdfDeclareGraphicsRule{.pdf}{png}{.png}{convert -density 200 #1 \OutputFile}

@@

\date[IJCAI '13]{
IJCAI '13
}

@@

%\begin{frame}{Outline}
%  \tableofcontents
%  % You might wish to add the option [pausesections]
%\end{frame}

@@

\begin{frame}
Pose as a sequential decision making problem (\emph{pool-based active learning}):
\begin{itemize}
\item<1-> No measurements available in advance, just a set (pool) of possible\\sampling locations ($D$)
\vspace{0.5em}
\item<2->[]\hspace{-1.5em} At each iteration $t \geq 1$:
\item<2-> Decide where to measure next ($\*x_t \in D$)
\item<3-> Obtain noisy observation ($y_t = f(\*x_t) + n_t$)
\item<4-> Update our estimate of $f$
\end{itemize}
%\begin{center}
%\color{white}
%\includegraphics<1>[draft,width=4.45in]{figures/oned_0}
%\color{black}
%\includegraphics<2>[width=4.45in]{figures/oned_0}
%\includegraphics<3>[width=4.45in]{figures/oned_1_0}
%\includegraphics<4>[width=4.45in]{figures/oned_1_1}
%\includegraphics<5>[width=4.45in]{figures/oned_1_2}
%\includegraphics<6>[width=4.45in]{figures/oned_2_0}
%\includegraphics<7>[width=4.45in]{figures/oned_2_1}
%\includegraphics<8>[width=4.45in]{figures/oned_2_2}
%\end{center}
\end{frame}

@@

%\begin{frame}
%\begin{center}
%\uncover<1->{\large Why GPs are nice}
%\end{center}
%\begin{itemize}
%\item<2-> \textbf{Nonparametric}:\\
%      Impose ``smoothness'' assumptions via kernel $k(x, x')$.
%\vspace{1em}
%\item<3-> \textbf{Bayesian}, yet \textbf{efficient}:
%      \begin{align*}
%        \mu_t(\*x) &= \*k_t(\*x)^T\left(\*K_t + \sigma^2 \*I\right)^{-1}\*y_t\\
%        k_t(\*x, \*x') &= k(\*x, \*x') - \*k_t(\*x)^T\left(\*K_t + \sigma^2 \*I\right)^{-1}\*k_t(\*x)\notag\\
%        \sigma_t^2(\*x) &= k_t(\*x, \*x)
%      \end{align*}
%      Suitable for step-by-step updates.
%\vspace{1em}
%\item<4-> They provide \textbf{variance estimates}!\\
%          Construct confidence intervals: $Q_t(\*x) = \left[\mu_{t-1}(\*x) \pm \beta_t^{1/2} \sigma_{t-1}(\*x)\right]$
%\end{itemize}
%\end{frame}

\begin{frame}
\begin{center}
\large Gaussian processes
\end{center}
\begin{itemize}
\item<1-> \textbf{Nonpaparametric}: impose ``smoothness'' assumptions via kernel $k(\*x, \*x')$
\item<2-> Mean \textbf{and variance} estimates: construct confidence intervals $Q_t(\*x)$
\item<7-> \textbf{Bayesian}, yet \textbf{efficient}: suitable for step-by-step updates
\end{itemize}
\begin{center}
\color{white}
\includegraphics<1-2>[draft,width=4in]{figures/voned_0_0}
\color{black}
\includegraphics<3>[width=4in]{figures/voned_0_0}
\includegraphics<4>[width=4in]{figures/voned_0_1}
\includegraphics<5>[width=4in]{figures/voned_0_2}
\includegraphics<6-7>[width=4in]{figures/voned_0_3}
\includegraphics<8>[width=4in]{figures/voned_1_0}
\includegraphics<9>[width=4in]{figures/voned_1_1}
\includegraphics<10>[width=4in]{figures/voned_1_2}
\includegraphics<11>[width=4in]{figures/voned_2_0}
\includegraphics<12>[width=4in]{figures/voned_2_1}
\includegraphics<13>[width=4in]{figures/voned_2_2}
\includegraphics<14>[width=4in]{figures/voned_3_0}
\includegraphics<15>[width=4in]{figures/voned_3_1}
\includegraphics<16>[width=4in]{figures/voned_3_2}
\end{center}
\end{frame}

\begin{frame}
\begin{enumerate}
\item<1-> How do we \textbf{estimate} the function? \uncover<3->{\Large\color{green!70!black}\checkmark}
\vspace{0em}
\item<4-> How do we \textbf{classify}? \uncover<14->{\Large\color{green!70!black}\checkmark}
\vspace{0.3em}
\item<15-> How do we \textbf{select} ``informative'' measurements? \uncover<22->{\Large\color{green!70!black}\checkmark}
\uncover<16->{
\begin{itemize}
\item<16-> Pick among the yet unclassified\ldots
\item<17-> \ldots the most ``ambiguous'' point
           \uncover<21->{(max. variance or random also work)}
\end{itemize}}
\end{enumerate}

\begin{center}
\color{white}
\includegraphics<1>[draft,width=3.7in]{figures/voned_cl_00}
\color{black}
\includegraphics<2-4>[width=3.7in]{figures/voned_cl_00}
\includegraphics<5>[width=3.7in]{figures/voned_cl_01}
\includegraphics<6>[width=3.7in]{figures/voned_cl_10}
\includegraphics<7>[width=3.7in]{figures/voned_cl_11}
\includegraphics<8>[width=3.7in]{figures/voned_cl_20}
\includegraphics<9>[width=3.7in]{figures/voned_cl_21}
\includegraphics<10>[width=3.7in]{figures/voned_cl_30}
\includegraphics<11>[width=3.7in]{figures/voned_cl_31}
\includegraphics<12>[width=3.7in]{figures/voned_cl_40}
\includegraphics<13-17>[width=3.7in]{figures/voned_cl_41}
\includegraphics<18>[width=3.7in]{figures/voned_cl_41_amb_0}
\includegraphics<19>[width=3.7in]{figures/voned_cl_41_amb_1}
\includegraphics<20->[width=3.7in]{figures/voned_cl_41_amb_2}
\end{center}
\end{frame}

@@

\begin{frame}
\begin{columns}[t]
\column{0.45\textwidth}
{\footnotesize
\begin{algorithmic}
  \REQUIRE sample set $D$, GP prior ($\mu_0$, $k$, $\sigma_0$),\\
           \hspace{2.2em}thr. value $h$, accuracy parameter $\epsilon$
  \ENSURE predicted sets $\hat{H}$, $\hat{L}$
  \uncover<2->{
  \CSTATE{c1}$H_0 \gets \varnothing$,\enskip $L_0 \gets \varnothing$,\enskip $U_0 \gets D$ \label{lin:init1}
  %\LET{$H_0$}{$\varnothing$} \label{lin:init1}
  %\LET{$L_0$}{$\varnothing$}
  %\LET{$U_0$}{$D$}
  \CLET{c1}{$C_0(\*x)$}{$\mathbb{R}$, for all $\*x \in D$} \label{lin:init2}
  \CLET{c1}{$t$}{1}
  }
  \uncover<3->{
  \CWHILE{c6}{$U_{t-1} \neq \varnothing$}
    \CSTATE{c6}$H_t \gets H_{t-1}$,\enskip $L_t \gets L_{t-1}$,\enskip $U_t \gets U_{t-1}$
    }
    %\LET{$H_t$}{$H_{t-1}$}
    %\LET{$L_t$}{$L_{t-1}$}
    %\LET{$U_t$}{$U_{t-1}$}
    \uncover<4->{
    \CFORALL{c2}{$\*x \in U_{t-1}$}
      \CLET{c2}{$C_{t}(\*x)$}{$C_{t-1}(\*x) \cap Q_t(\*x)$} \label{lin:upd}
      \CIF{c2}{$\min(C_t(\*x)) + \epsilon > h$} \label{lin:class1}
        \CLET{c2}{$U_t$}{$U_t \setminus \{\*x\}$}
        \CLET{c2}{$H_t$}{$H_t \cup \{\*x\}$} 
      \CELSIF{c2}{$\max(C_t(\*x)) - \epsilon \leq h$} \label{lin:classr2}
        \CLET{c2}{$U_t$}{$U_t \setminus \{\*x\}$}
        \CLET{c2}{$L_t$}{$L_t \cup \{\*x\}$}
      \CENDIF{c2} \label{lin:class2}
    \CENDFOR{c2}
    }
    \uncover<5->{
    \CLET{c3}{$\*x_t$}{$\argmax \{a_t(\*x)\mid \*x \in U_t\}$} \label{lin:sel1}
    \CLET{c3}{$y_t$}{$f(\*x_t) + n_t$} \label{lin:sel2}
    }
    \uncover<6->{
    \CSTATE{c4}Compute $\mu_t(\*x)$ and $\sigma_t(\*x)$, $\forall\*x \in U_t$ \label{lin:inf}
    }
    \uncover<3->{
    \CLET{c6}{$t$}{$t + 1$}
  \CENDWHILE{c6}
  }
  \uncover<2->{
  \CLET{c5}{$\hat{H}$}{$H_{t-1}$} \label{lin:ret1}
  \CLET{c5}{$\hat{L}$}{$L_{t-1}$} \label{lin:ret2}
  }
\end{algorithmic}
}
\column{0.55\textwidth}
\begin{center}
The Level Set Estimation (\acl) algorithm
\end{center}
\only<3-6>{\vspace{34pt}$\leftarrow$ {\small loop until all points have been classified\\}\vspace{40pt}}
\only<4-6>{$\leftarrow$ {\small classify\\}\vspace{52pt}}
\only<5-6>{$\leftarrow$ {\small select max. ambiguity point\\}\vspace{3pt}}
\only<6>{$\leftarrow$ {\small update GP estimate}}
\only<7->{
\vspace{3pt}
\begin{itemize}
\only<7->{
\item Monotonicity of
\begin{enumerate}
\item confidence intervals
\item classification
\end{enumerate}
}
\vspace{0em}
\only<8->{
\item Relaxed classification rules by an accuracy parameter $\epsilon$\\
      (trades off sampling cost for accuracy)
}
\end{itemize}
}
\begin{center}
\includegraphics<8->[width=2.5in]{figures/voned_cl_41_eps}
\end{center}
\end{columns}
\end{frame}

@@

\subsection*{Results}
\begin{frame}
\begin{center}
{\large Experiments}
\end{center}
\begin{enumerate}
\item \acl
\item<2-> Maximum variance sampling:
\vspace{-0.5em}
\begin{align*}
\*x_t = \argmax_{\*x\in D} \sigma_{t-1}(\*x)
\end{align*}
\item<3-> State of the art ``straddle'' heuristic (Bryan \emph{et al.}, 2005):
\vspace{-0.5em}
\begin{align*}
%\*x_t &= \argmax_{\*x\in D} 1.96\sigma_{t-1}(\*x)-|\mu_{t-1}(\*x) - h|\\
\*x_t \approx \argmax_{\*x\in D} a_{t-1}(\*x) \tag{for $\beta_t^{1/2} = 1.96$}
\end{align*}
\end{enumerate}
\end{frame}

\begin{frame}
\begin{center}
\hspace{4pt}\includegraphics<1->[width=4in]{figures/limno_chl_ls}\\[0.5em]
\uncover<2->{\includegraphics[width=2.4in]{figures/ev_chl_eps}}
\uncover<3->{\includegraphics[width=2.25in]{figures/ev_chl_seq}}
\end{center}
\end{frame}

\begin{frame}
\begin{center}
\includegraphics<1->[width=4in]{figures/limno_bgape_ls}\\[0.5em]
\color{white}
\only<1>{\includegraphics[draft,width=2.3in]{figures/ev_bgape_seq}}
\color{black}
\only<2>{\includegraphics[width=2.3in]{figures/ev_bgape_seq}}
%\color{white}
%\only<2>{\includegraphics[draft,width=2.3in]{figures/ev_bgape_eps}}
%\color{black}
%\only<3>{\includegraphics[width=2.3in]{figures/ev_bgape_eps}}
%\only<4>{\includegraphics[width=2.3in]{figures/ev_bgape_seq_str_sc}}
%\only<5>{\hspace{-16pt}\includegraphics[width=3.77in]{figures/limno_bgape_class_354}}
%\only<6>{\hspace{-16pt}\includegraphics[width=3.77in]{figures/limno_bgape_str_class_400}}
%\only<7>{\hspace{-16pt}\includegraphics[width=3.77in]{figures/limno_bgape_var_class_400}}
\end{center}
\end{frame}

@@

\begin{frame}
\begin{itemize}
\item<1-> What if we don't know the threshold level $h$?
\vspace{1em}
\item<2-> Implicitly define $h = \omega \max_{\*x\in D} f(\*x),\ 0 < \omega < 1$
\vspace{1em}
\item<3-> No existing algorithms for this problem (to our knowledge)
\vspace{1em}
\item<4-> We extend \acl (and its theory!) to this setting
\vspace{1em}
\item<5->\iacl algorithm:
\begin{itemize}
\item<6-> Need to accurately estimate the maximum $\rightarrow$ modified selection rule
\item<7-> $h$ is now an estimated quantity $\rightarrow$ modified classification rules
\end{itemize}
\end{itemize}
\begin{center}
%\color{white}
%\only<1-2>{\includegraphics[draft,width=3.77in]{figures/voned_cl_41_imp_1}}
%\color{black}
%\only<3>{\includegraphics[width=3.77in]{figures/voned_cl_41_imp_1}}
%\only<4->{\includegraphics[width=3.77in]{figures/voned_cl_41_imp_2}}
\end{center}
\end{frame}

@@

\begin{frame}
\begin{itemize}
\item<1-> Up to this point we have assumed a fixed cost per sample
\item<2-> What about the traveling distance between measurements?
\item<3-> We extend \acl to select a \emph{batch} of sampling locations at each step (\bacl)
\item<3-> Use this to plan ahead:
\begin{itemize}
\item Select a batch of sampling locations
\item Connect them using a Euclidean TSP path
\item Traverse path and collect measurements
\end{itemize}
\end{itemize}

@@

\begin{frame}
\begin{center}
\large Come to the poster session for more\ldots
\end{center}
\begin{itemize}
\item<2-> \ldots theory: sample complexity bounds in more detail
\item<3-> \ldots applications: estimate world regions of low internet latency\\[0.5em]
\hspace{3em}\includegraphics[height=2in]{figures/map}
\item<4-> \ldots results: why does \acl greatly outperform ``straddle'' in some cases?
\end{itemize}
\end{frame}
%\begin{itemize}
%\item<1-> Which world regions have low enough latency (e.g. < $150$ ms)
%      for video chatting, online gaming, etc.?
%\item<2-> Ideal setting for batch sampling $\rightarrow$ multiple pings in parallel
%\end{itemize}
%\begin{center}
%\color{white}
%\includegraphics<1-2>[draft,height=2.5in]{figures/map}
%\color{black}
%\includegraphics<3>[height=2.5in]{figures/map}
%\includegraphics<4>[height=2.5in]{figures/map_ls_150}
%\end{center}

@@

%\begin{frame}
%\begin{center}
%\large Questions?\\
%\vspace{2em}
%\sig{\includegraphics[width=3.5in]{figures/dilbert}}{www.dilbert.com}
%\end{center}
%\end{frame}
